`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`

### 2025-07-02 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/01_reference-aggregation.Rmd
plot fixes

---
title: "`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  sample_id: "SCPCS000105"
  library_id: "SCPCL000122"
---

@@

Read SCE object so we can get UMAP and consensus cell types:

@@

sce_df <- readRDS(sce_file) |>
  scuttle::makePerCellDF() |>
  tibble::as_tibble() |>
  dplyr::select(
    barcodes,
    consensus_annotation = consensus_celltype_annotation,
    UMAP1 = UMAP.1,
    UMAP2 = UMAP.2
  )
```

@@

sce_df <- sce_df |>
  dplyr::left_join(singler_df, by = "barcodes") |>
  dplyr::left_join(validation_df, by = "consensus_annotation") |>
  # set validation NA -> Unknown
  dplyr::mutate(
    validation_group_annotation =
      ifelse(is.na(validation_group_annotation), "Unknown", validation_group_annotation)
  )
```

@@

plot_delta_median(aggr, agree_barcodes, plot_title = "Aggregated delta_median") +
  plot_delta_median(non_aggr, agree_barcodes, plot_title = "Non-aggregated delta_median") &
  theme(legend.position = "none")
```

@@

```{r}
calculate_confusion(
  sce_df,
  "aggregated",
  "not_aggregated"
)
```

@@

```{r, fig.height = 8}
make_jaccard_heatmap(
  sce_df,
  "aggregated",
  "not_aggregated",
  "Aggregated labels",
  "Non-aggregated labels"
)
```

@@

```{r, fig.height = 10}
make_jaccard_heatmap(
  sce_df,
  "consensus_annotation",
  "aggregated",
  "OpenScPCA Consensus cell type validation group",
  "Aggregated labels"
)
```

@@

```{r, fig.height = 10}
make_jaccard_heatmap(
  sce_df,
  "consensus_annotation",
  "not_aggregated",
  "OpenScPCA Consensus cell type validation group",
  "Non-aggregated labels"
)
```

>>>>

---
title: "`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`"
author: "Stephanie J. Spielman"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 3
    code_folding: hide
params:
  sample_id: "SCPCS000109"
  library_id: "SCPCL000126"
---

@@

Read SCE object so we can get consensus cell types:

@@

celltype_df <- readRDS(sce_file) |>
  colData() |>
  tibble::as_tibble() |>
  dplyr::select(
    barcodes,
    consensus_annotation = consensus_celltype_annotation
  )
```

@@

celltype_df <- celltype_df |>
  dplyr::left_join(singler_df, by = "barcodes") |>
  dplyr::left_join(validation_df, by = "consensus_annotation") |>
  # set validation NA -> Unknown
  dplyr::mutate(
    validation_group_annotation =
      ifelse(is.na(validation_group_annotation), "Unknown", validation_group_annotation)
  )
```

@@

plot_delta_median(aggr, agree_barcodes, plot_title = "Aggregated delta_median") +
  plot_delta_median(non_aggr, agree_barcodes, plot_title = "Non-aggregated delta_median") +
  plot_layout(guides = "collect") & theme(legend.position = "bottom")
```

@@

```{r}
calculate_confusion(
  celltype_df,
  "aggregated",
  "not_aggregated"
)
```

@@

```{r, fig.height = 8, fig.width = 8}
make_jaccard_heatmap(
  celltype_df,
  "aggregated",
  "not_aggregated",
  "Aggregated labels",
  "Non-aggregated labels"
)
```

@@

```{r, fig.height = 8, fig.width = 8}
make_jaccard_heatmap(
  celltype_df,
  "validation_group_annotation",
  "aggregated",
  "OpenScPCA Consensus cell type validation group",
  "Aggregated labels"
)
```

@@

```{r,fig.height = 8, fig.width = 8}
make_jaccard_heatmap(
  celltype_df,
  "validation_group_annotation",
  "not_aggregated",
  "OpenScPCA Consensus cell type validation group",
  "Non-aggregated labels"
)
```
